\subsection{Functional Requirements}
    \begin{enumerate}
        \item R101 The system shall provide user with an interactive interface to login into the app.
        \item R102 The system shall provide user with the ability to search other users.
        \item R103 The system shall provide super admin and office staff with the ability to insert, update and delete information regarding batches, courses, semesters, subject, topics, subtopics.
        \item R104 The system shall provide user to view syllabus.
        \item R105 The system shall provide it users with information about the completed topics.
        \item R106 The system shall provide the three admins with the ability to schedule lectures.
        \item R107 The system shall provide user with the information regarding lecture schedules, attendance, syllabus.
        \item R108 The system shall provide students the ability to mark their attendance with their RFID card and Fingerprint.
        \item R109 The system shall provide the three admins the ability to register student's attendance.
        \item R110 The system shall provide the users with interactive report of student's attendance as per lecture or as per student of a particular batch's semester's subject.
        \item R111 The system shall provide super admin and office staff with the ability to block a student's account.
        \item R112 The system shall provide the super admin to manage their own profile.
        \item R113 The system shall provide the super admin and office staff the ability to manage student's profile.
        \item R114 The system shall provide the three admins to manage their own general profile.
        \item R115 The system shall provide the student with the ability to manage their general profile
        
    \end{enumerate}

